%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}





%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \href{https://portfolio.mkpatidar.in/}{\Huge \scshape   Mayank Patidar} \\ \vspace{1pt}
    Indore, Madhya Pradesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-8959050275 ~ 
    \href{https://portfolio.mkpatidar.in/}{\raisebox{-0.2\height}\faUser\  
    {Portfolio}} ~ 
    \href{mailto:mayankpatidar275@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {mayankpatidar275@gmail.com}} ~ 
    \href{https://linkedin.com/in/mkpatidarr/}{\raisebox{-0.2\height}\faLinkedin\ {LinkedIn}}  ~
    \href{https://github.com/mayankpatidar275}{\raisebox{-0.2\height}\faGithub\ {GitHub}}  ~
    \href{https://leetcode.com/u/mkpatidar/}{\raisebox{-0.2\height}\faExternalLink\ {LeetCode}}
    \vspace{-8pt}
\end{center}

\vspace{6pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{http://sellthruagency.com/}{SellThru }}{March 2026 -- Present}
      {Software Developer}{\href{}{}}
    \resumeItemListStart
    \resumeItem{Architected a multi-service \textbf{MCP} server on a VPS, integrating
    \textbf{Claude AI} with GA4, GSC, Google ads, Meta ads and DataForSEO - enabling the 30-person team to                                                                      
    query marketing data directly in Claude, saving \textbf{~20 hours/week}.}
    \resumeItem{Maintained client websites using Shopify and Webflow; implemented                                                                        
    analytics tracking via Google Tag Manager.}
    % \resumeItem{\textbf{Tech}: Python, Google tag manager, GA4, GSC, Shopify, Webflow.}
    \resumeItemListEnd

      \resumeSubheading
      {\href{https://www.envo.club/}{Envo Climate Technologies Ltd. }}{March 2025 -- Feb 2026}
      {Software Developer}{\href{}{}}
      \resumeItemListStart
        %  \resumeItem{Developed envo dashboard for B2B clients like \textbf{Mercedes Benz}.}
        \resumeItem{%
          \href{https://apps.apple.com/us/app/envo/id6746687785}{\textbf{iOS}\,\raisebox{-0.1\height}{\faExternalLink}} \quad
          \href{https://play.google.com/store/apps/details?id=com.app.clubenvo}{\textbf{Android}\,\raisebox{-0.1\height}{\faExternalLink}}  \quad - 
          Building and maintaining cross-platform \textbf{mobile apps}, ensuring GDPR compliance.
        }
    \resumeItem{Led a team of 2 engineers, ensuring high-quality, maintainable code through thorough PR reviews and clean merges.}
    \resumeItem{Designed and implemented key product features - rewards, streaks, challenges, push notifications, referral invites, email delivery, abuse prevention and envo dashboard for B2B clients like \textbf{Mercedes Benz}.}
    \resumeItem{Built Mixpanel \textbf{analytics} to track user behavior, reach, activation, engagement, and retention; defined
    KPIs and funnels for data-driven growth.}
    \resumeItem{Integrated \textbf{Generative AI} (Gemini) to validate user posts, extract structured data, and auto-generate emotionally resonant messages to boost engagement.}
    \resumeItem{Architected a secure, B2B/B2C-ready \textbf{multi-tenant} backend with RLS-based access control, isolated environments, and automated CI/CD pipelines.}
    \resumeItem{%
      \href{https://apps.apple.com/in/app/gud-for-us-clean-food-ai/id6755870992}{\textbf{iOS}\,\raisebox{-0.1\height}{\faExternalLink}} \quad
      \href{https://play.google.com/store/apps/details?id=com.app.gudforus&hl=en_IN}{\textbf{Android}\,\raisebox{-0.1\height}{\faExternalLink}} \quad -
      Built the backend for \textbf{GudForUs}, an AI-powered clean food scanner app; handles barcode-based product lookup, personalized health scoring, and ingredient safety analysis using Generative AI.
    }
    \resumeItem{\textbf{Tech}: Node.js, Gemini API, Supabase, AWS (ECS Fargate, Amplify, S3), Expo, React Native, Mantine UI.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://docs.google.com/document/d/14UAPdOMhaYQoPYvbmsXqfiF_XbRUYK8oPJLTD1LN1Xs/edit?usp=sharing}{ThinkMetal Pvt. Ltd. (100X.VC)}}{Dec 2023 -- Feb 2025}
      {Software Developer}{Chennai, Tamil Nadu}
      \resumeItemListStart

      \resumeItem{\textbf{Implemented features} such as 3D model rotation and face highlighting on hover; refactored styling and fixed bugs to ensure a stable, reliable, and repeatable desktop application.}

      \resumeItem{Built and deployed the \textbf{Admin Panel} dashboard from scratch to manage 3D printers, users, software, and access controls; integrated \textbf{OAuth 2.0}.}
      
      % \resumeItem{Enhanced the \href{https://thinkmetal.in}{\textbf{website}} by implementing design-driven updates and improvements.}
     
     \resumeItem{Developed the 3D printer controller screen frontend from scratch.}

     \resumeItem{\textbf{System design} and development of the Over-the-air (OTA) update system for industrial 3D printers.}

     \resumeItem{Migrated the printer backend from JavaScript to Go, boosting performance and enabling a secure standalone build.}
     
     \resumeItem{Managed backend deployment on Raspberry Pi, Lattepanda and AWS; automated deployments and server setup using shell scripting to improve developer experience and ops efficiency.}

    \resumeItem{Self-hosted Highlight (Sentry alternative) for session replay, full-stack error monitoring, and advanced logging.}

    \resumeItem{\textbf{Tech}: React.js, Tauri, Next.js, TanStack, React Router, Context API, Module CSS, Shadcn, Tailwind, Socket.IO, Zod, Three.js, React Three Fiber, Express.js, MongoDB, Prisma, PostgreSQL, PM2, SSH, Github Workflows, Linux, Docker.}

\resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PRODUCTS-----------
\section{Products}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://relivchats.com}{\textbf{Reliv Chats}\,\raisebox{-0.1\height}{\faExternalLink}} $|$ \emph{Next.js, FastAPI, Python, PostgreSQL, Qdrant, Gemini AI, Razorpay, Celery, Redis, Docker, RAG}}{2025}
      \resumeItemListStart
        \resumeItem{Independently designed, built, and launched a production \textbf{AI SaaS} that analyzes WhatsApp conversations (romantic, friendship, family, work) and generates psychological relationship insights.}
        \resumeItem{Generates free instant stats (message patterns, emoji analysis, response times) on upload, with paid AI-powered deep insights unlocked via credits;
  shareable insight cards for virality.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Go, JavaScript, TypeScript, SQL} \\
     
     \textbf{Technologies/Frameworks}{: HTML, CSS, React.js, Redux, Context API, Next.js, Node.js, REST API, Git/GitHub, Express.js, Docker, Tailwind, Webpack, Rollup, SCSS, Firebase.} \\
     
     \textbf{Concepts}{: Data Structures and Algorithms,  Object Oriented Programming, Systems Design, Database Management System, Operating System, Computer Networks, Blockchain} \\
     
    }}
 \end{itemize}
%  \vspace{-16pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology, Nagpur}{2020 --  2024}
      {Bachelor of Technology in ECE}{Maharashtra}
  \resumeSubHeadingListEnd


\end{document}
